---
title: "02_HW_Sampling_Simulation"
author: "Hannah Stroud"
date: "September 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Sampling and Simulation

```{r}
library(dplyr)
library(magrittr)
```

### 1. R Warmup 

#### 1a. Create a vector of 100 randomly distrubuted numbers 
```{r} 
   my_vec <- runif(100, min=0, max=100)
      str(my_vec)
      summary(my_vec)
```
      
str gives information on the vector itself so tells you its a numeric vector and the number of elements  
summary gives information about the values in the vector- so it gives the Min, Max, Median and quartiles.  
     
#### 1b. Plotting with hist
```{r}
hist(my_vec)
```   
hist(my_vec) plots the frequency of each bin, with a bin size of 10
The helpfile gives the default arguments if all you enter in the () is the vector, and defines each parameter argument.  
    
####1c. mtcars 
```{r}
 data(mtcars)
    class(mtcars)
    str(mtcars)
    summary(mtcars)
```

class tells use mtcars is a data frame, str gives information about the dataframe- ie variables and number of observations, summary gives quartiles of each variable  

####1d. Looking up data.frame
Data frames are collections of variables, like lists or matrices. Rows have unique names, each row is a variable with a set of observations.   

###2. Sample Properties

```{r}
vole_vaso <- c(98,96,94,88,86,82,77,74,70,60,
               59,52,50,47,40,35,29,13,6,5) 
```
####2a. Say vole vasopressin 10 times fast as you can
    I tripped up twice  
   
####2b.
```{r}    
     #mean
      mean(vole_vaso)
     #median
      median(vole_vaso)
     #standard deviation
      sd(vole_vaso)
     #interquartile range
      IQR(vole_vaso)  
```
####2c. Standard Error of Mean 
```{r}
       sem <- sd(vole_vaso)/sqrt(length(vole_vaso))
      sem 
```

####2d. 
The standard error of mean tells us that our mean is fairly precise for giving the average level of vassopressin in the population.  

### 3. Sample Size for upper quartiles 
```{r}
quantile(vole_vaso, probs = 0.75)
```
####3a. 
```{r}  resamp <- sample(vole_vaso, 10, replace=TRUE)```

#### 3b.Build Initial Data Frame
```{r} 
vole_sim <- data.frame(samp_size= rep(5:20, time=100))
```


#### 3c. Simulate upper quartiles for each sample size
```{r} 
vole_sim_uq <- vole_sim %>% 
  rowwise() %>%
mutate(upp_qnt= quantile(sample(vole_vaso, size=samp_size, replace=TRUE),probs=0.75))
```
#### 3d. Plot to estimate best sample size 
```{r}
plot(upp_qnt~samp_size, data=vole_sim_uq)
```
Best sample size would be around 17 samples.  
    
### 4. SE and CI
####4a. 
```{r}
stnd_err_upper_quant <- vole_sim_uq %>%
  group_by(samp_size)%>%
  summarize(sd_up_qnt= sd(upp_qnt), avg_upp_quant= mean(upp_qnt)) %>% 
  ungroup()
```
####4b.The meaning of the standard error 
The standard error of the upper quantile tells use the distribution of standard errors  
####4c. Confidence interval
```{r}
stderr_10 <- stnd_err_upper_quant[6,2] 
avg_u_qt_10 <-stnd_err_upper_quant[6,3]
CI_10 <- 2*stderr_10
CI_uq_lower <- avg_u_qt_10 - CI_10/2
CI_uq_upper <- avg_u_qt_10 + CI_10/2 
```

####4d. Extra Credit Extra Credit: Instead of having each sim calculate a upper quartile, and then sifting down to the SE of that upper quartile (or the CI), have each simulation calculate a CI. Then, for just a sample size of 10, how many CI's contain the true value of 83?
```{r}
# simulation that directly gives CI
# CI= 2*Standard Error
# standard error= standard deviation of your estimates 
# standard deviation= measure of dispersion 

vole_sim_CI <- vole_sim_uq %>% #take the upper quartile data already have
  group_by(samp_size)%>%
  summarize(uq_se = sd(upp_qnt), uq_avg= mean(upp_qnt)) %>%
  mutate(CI= 2*uq_se) %>%
  ungroup()
vole_sim_CI
```
95 confidence intervals contain the true value of 83  

